Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/paper.tex
Add UBC acks

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast evaluation. The research was
  supported by Centers for Disease Control and Prevention (CDC) grant
  U01IP001121, gifts from Facebook, Google, McCune, and Optum, and National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE175016.}

>>>>

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast evaluation. The research was
  supported by Centers for Disease Control and Prevention (CDC) grant
  U01IP001121; gifts from Facebook, Google, McCune, and Optum; the National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE175016; the Canadian Statistical Sciences Institute; and the National
  Sciences and Engineering Research Council of Canada (NSERC) RGPIN-2021-02618.}
